
The following list documents what I have read on the topic and felt worth keeping a record of. While I haven't added anything I didn't find useful in one way or another, many of the sources listed here may not be of interest to many people.

*(This page remains work in progress. I use keywords to generate headings and sub-headings for this list. I often assign more than one keyword to a source, which I do on purpose. What I don't do on purpose is attached the wrong keyword to a source. But it happens, with the consequence that a source ends up under a headline it doesn't belong to. I remain hopeful that I will spot these mistakes over time. Please [email](mailto:alexander.reppel@rhul.ac.uk?subject=BibtexFile--) suggestions on how to improve this list.)*


```{r message=FALSE, warning=FALSE, include=FALSE}
library(RefManageR)
library(bibtex)
```


```{r message=FALSE, warning=FALSE, include=FALSE}
if (!exists("library")) {
  library <- "assets/references/example.bib"
}
bib <- RefManageR::ReadBib(library, check = "error")  
```


```{r message=FALSE, warning=FALSE, include=FALSE}
# Extract first and second order keywords
topics <- c()
categories <- c()
```


```{r message=FALSE, warning=FALSE, include=FALSE}
for (i in 1:length(bib$keywords)) {
  if (grepl(",", bib$keywords[[i]], fixed=TRUE)) {
    x <- "," } else {
      x <- ";"
    }
  kwds <- as.list(
    unlist(strsplit(bib$keywords[[i]], x)))
  for (j in 1:length(kwds)) {
    if (!startsWith(kwds[[j]], "___")) {
      cats <- as.list(unlist(strsplit(kwds[[j]], "--")))
      if (length(cats) > 1) {
          t <- trimws(cats[[2]])
          c <- trimws(cats[[1]])
      topics <- append(topics, t)
      categories <- append(categories, c)
        }
    }
  }
  }
```


```{r message=FALSE, warning=FALSE, include=FALSE}
topics <- unique(sort(na.omit(topics)))
categories <- unique(sort(na.omit(categories)))
```


## Topics

```{r navigation, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
navigation <- c()
for (t in 1:length(topics)) {
  if (!t == length(topics)) {
    knitr::asis_output(cat(paste0("[", topics[t], "][], ")))
  } else {
    knitr::asis_output(cat(paste0("[", topics[t], "][].")))
  }
}
```


```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
for (t in 1:length(topics)) {
  if (!t == 1) {
    cat("<div style='text-align: right'>*([Back to list of topics][Topics])*</div>\n")
  }
  cat(paste0("\n## ", topics[t], "\n"))
  for (c in 1:length(categories)) {
    keyword <- paste(categories[c], "--", topics[t])
    b <- bib[keywords = keyword]
    if (length(b) > 0) {
      cat(paste0(
        "\n### ", topics[t], ": ", categories[c], "\n"))
      print(
        b,
        .opts = list(
          style = "markdown",
          bib.style = "authoryear",
          max.names = 3,
          first.inits = FALSE))
    }
  }
}
```

